Bird beak's elaboration and innovation

### 2022-07-13 Analysis/04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd
Update 04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd

>>>>

## Overlapping ellipses plot

```{r}
load("../Data/Processed/tip_colours_super_orders.rda")
load("../Data/Processed/tip_colours_orders.rda")

## Matching colours (fast utility)
match.col <- function(data, col) {
    return(c(col[match(names(size.subsets(data)), names(col))[-length(size.subsets(data))]], "grey"))
}

pdf(file = "../Manuscript/Figures/Figure_supplementary_aligned_ellipses.pdf", height = 6, width = 12)
par(mfrow = c(1,2))
## Plotting the aligned and scale ellipses for the superorders
covar.plot(superorder_shapespace, ellipses = mean,
           col = match.col(superorder_shapespace, tip_colours_super_orders),
           legend = TRUE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_super_orders)), 3),
           main = "Scaled and centred average super order VCV")

## Plotting the aligned and scale ellipses for the superorders
covar.plot(order_shapespace, ellipses = mean,
           col = match.col(order_shapespace, tip_colours_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_orders)), 3),
           main = "Scaled and centred average order VCV")
dev.off()
```
